\thetitle

### 2017-12-17 TeX/manuscript.tex
made a possible diagram for combining the two computations

(a tree which models a situation where logical and numerical information need to be combined via some operator) \textcolor{red}{- What sort of situation REQUIRES this?}

>>>>

(a tree which models a situation where logical and numerical information need to be combined via some operator) \textcolor{red}{- What sort of situation REQUIRES this? (TemperatureTree is a possibility)}
